Optimization of wide-band quasi-omnidirectional 1-D photonic structures

### 2021-01-20 PaperVictor.tex
Revise Victor et al. revisions.

The function
$f_{3}$ yields after optimization the highest $\braket{R}$ in the
region $\mathcal R_1$ with the thinnest structure (see table
\ref{tab:tableA}). Furthermore, this structure has a calculated OD gap
\notaL{I'm unsure about the nomenclature ``gap''. I guess it is
  theoretical, right?}
 \notaV{Podr\'{i}a utilizar el t\'{e}rmino "OD width" para referirme al ancho omnidireccional del espejo}
of 250 nm centered at 1125 nm with a
reflectance
$R>0.90$, as shown in Fig. \ref{Fig1}(b). We
synthesized a structure  designated {\em sample $S_1$} corresponding
to these results. For the region $\mathcal R_2$ the
resulting structures have similar thicknesses and attain similar reflectance
spectra, though the one with the smallest thickness and the maximum
reflectance is that obtained from the family $f_{1}$. We
also synthesized the corresponding
structure and designated it {\em sample $S_2$}. The
calculated optimized reflectance spectrum is shown in Fig. \ref{Fig1}(d).
This structure has a very wide region where $ R(\lambda, \theta)>
0.90$, which goes from 850 to 3000 nm in an angular range
from $0^\circ$ to $70^\circ$. Thus, it has a
quasi-OD (q-OD) gap of 2150 nm centered at 1925 nm.
The functions $f_i$ optimized for the region $\mathcal R_1$ are shown
in Fig. \ref{Fig1}(a), and those for $\mathcal R_2$
in Fig. \ref{Fig1}(c). The profiles $f_i$ are qualitatively
similar. For example, for $\mathcal R_1$ the optimal photonic
structures have a small number of periods tuned to the wavelengths where
silicon has a large absorption, i.e.,  the first periods of the
structure. 
\notaV{replanteo la idea: "For $\mathcal R_2$ it is only necessary that the periods have an adequate ordering.}
\notaL{No entendí qué hay que comentar en
  este caso} 
Due in $\mathcal R_2$, the absorption of porous silicon is negligible, the periods are distributed quasi-evenly.

@@

We measured the reflectance spectra of samples $S_1$ and $S_2$
at various angles of incidence $\theta$. Due to
experimental limitations, we restrict our results to the case of
unpolarized light. In Fig. \ref{Fig2}(a), the calculated and measured
reflectance corresponding to sample $S_1$ are compared from 350 to 1400 nm for different angles of
incidence ($\theta=10^\circ$, $20^\circ$, $30^\circ$, $40^\circ$,
$50^\circ$, and $60^\circ$). The spectra are qualitatively 
similar, and for $\lambda>700$ nm and $10^\circ < \theta < 
40^\circ$, they agree quantitatively, with a difference smaller 
than $5\%$.
\notaL{Yo no veo nada especial en 40 grados: and for
$\theta > 40^\circ$ both spectra are qualitatively consistent} \notaV{De acuerdo. Se puede omitir}
The
measured reflectance is lower than the calculated one, more so at
small wavelengths and large angles. This difference
may be partially attributed to the scattering of light due to the
roughness present at the sample
\cite{Theiss1994,Chavez2020,Ortiz2020} that we have not taken into
account in our theory. Due to the limitations of our
spectrophotometer, we couldn't perform measurements for $\theta>60^\circ$ and thus
check the OD gap. Nevertheless, our results allow us to conclude that
the structure has a quasi-omni-directional
bandgap (R$\left(\lambda,\theta \right)>0.90$) between 980 and
1340 nm.
\begin{figure}
	\label{Fig2}
	\begin{center}
		\includegraphics[width=\textwidth]{F2Alternativa.pdf}
	\end{center}
	\caption{Reflectance spectra for non-polarized light calculated and measured at different
	angles of incidence $\theta=10^\circ$, $20^\circ$, $30^\circ$,
        $40^\circ$, $50^\circ$, and $60^\circ$ for structure $S_1$
        (panel a)  and $S_2$ (panel b). The gray band indicates the
        region where the reflectance is greater than  $0.90$,
        corresponding to the quasi OD gap of the
        structure. Inset: photograph of the synthesized structure.}
\end{figure}
In Fig. \ref{Fig2}(b) we compare the
calculated and measured spectra of sample $S_2$ in the range
from 400 to 3000 nm.
Both spectra are very similar, with some differences at long
wavelengths which can be
attributed to an increase of imperfections such as wavy layers and
more roughness for deeper layers, due to a more restricted diffusivity
of the electrolyte as the thickness of the structure is increased
\cite{Negro2003,Vincent1993}. According to our results, this
structure has a wide quasi-omnidirectional gap ($R>0.90$) of 1800 nm
centered at 1880 nm.

@@

Another class of techniques for designing good reflectors across a wide spectral range
is to stack sub-mirrors tuned to different wavelengths chosen with
different criteria. 
\notaV{I rewrote this "For example, Agarwal et al. 
	\cite{Agarwal2003} proposed to stack sub-mirrors as follows: 
	tune the first sub-mirror to certain wavelength $\lambda_{1}$. 
	Tune subsequent submirrors $j$ to wavelengths $\lambda_j$, 
	chosen so that $\lambda_{j+1} + \lambda_{j}=2+j$."} 
For example, Agarwal et al. \cite{Agarwal2003} proposed a photonic 
structure in which she stacked 54 sub-mirrors as follows: the 
first sub-mirror consisted of 2.5 periods and tuned it to 
$\lambda_{1}=700$ nm; the following sub-mirrors were tuned to the 
wavelengths $\lambda_{j}$ according to the sequence $\lambda_{j+1} 
+ \lambda_{j}=2+j$ with 4 periods for each of the following 
periods.
\notaL{This cannot be correct. Please check}. Furthermore, Estrada-Wiese et al. \cite{DelRio2018}
developed a method that combines three stochastic optimization algorithms together with
a  narrow space search methodology to obtain a customized and optimized
PC configuration.

We recall that for a periodic structure, the propagation of
electromagnetic waves is described by the dispersion relation
\begin{equation}
	 \cos (KD) = \frac{1}{2} \text{Tr} \bm M,   \label{Dispersion}
\end{equation}
where $K$ is Bloch's vector, $\bm M$ the transfer matrix of a single
period of thickness $D$ \cite{Mochan1987, Mochan1988,
  Perez2018}. \notaL{Tr was already defined and the reference to the
  equation is wrong:  denotes the trace
and $M$ is the matrix given by Eq. \ref{MsBloch}}. \notaV{Entendido, gracias} Thus,
whenever $\left\vert\text {Tr} \left(M \right) \right\vert>2$
electromagnetic energy cannot propagate in the periodic system and we
expect a high reflectance for a finite system made of a finite number
of periods. This suggests the following design. We stack submirrors
each made of a few periods of a periodic system such that its photonic band gap
(PBG) overlaps the PBG of the previous and that of the next
submirror. The number of periods of each sub-mirror is an
important parameter. If it is too small, the sub-mirror would be
partially transparent within the PBG. If it is too large, the
resulting structure would be too thick. We followed two design
strategies: In the first, we considered sub-mirrors each with the same
number of periods. In the second, a different number of periods was
assigned to each submirrors with a PBG center within different
spectral regions: we used a single period for
$\lambda_{D}<500$ nm, two periods for $500 <\lambda_ {D} < 650$ nm
and three periods for $650<\lambda_ {D}<800$ nm.  and for
$\lambda_{D} \geq 800$ nm, the number of periods was variable.
\notaL{No se entiende. Los números uno, dos, tres ¿se sacaron de la manga? ¿se optimizaron? Para <800, ¿de dónde se sacó el número de periodos?}
\notaV{Los números de periodos uno, dos, tres, los eleg\'{i} para 
	que la estructura tenga pocos periodos en la region visible. 
	Adem\'{a}s, del c\'{a}lculo de las Trazas y reflectancias de 
	los subespejos individuales sintonizados de 1000 a 2500 nm, 
	tambi\'{e}n tienen una regi\'{o}n de propagaci\'{o}n prohibida 
	en el intervalo de 400 a 900 y la reflectancia es mayor al 
	80\%. Esto se puede observar en la Fig. SITrazasyRefSE.pdf}
In both designs, the optimal overlap of two consecutive PBGs was obtained that maximized reflectance.
\notaL{No quisiste decir average reflectance $\braket{R}$?. Si sí, en qué rango promediaste?} \notaV{Si, se promedi\'{o} en el siguiente rango}
Reflectance spectra were calculated for
$400\text{nm}\le \lambda\le 3000\text{nm}$ and for $0^\circ\le\theta\le90^\circ$.

Table \ref{tab:table2} shows the number of periods of each sub-mirror ($p$),
\notaL{Está difícil esta notación. ¿De dónde vienen la s y
  la e. $Np_{se}$ parece el producto de $N$ con $p_{se}$. ¿De dónde la p?} \notaV{Lo cambi\'{o} por $p$ de periods y $N$ de N\'{u}mero total de periodos}
the total number of stacked sub mirrors ($N_{se}$)
\notaL{El encabezado de la tabla está mal} \notaV{Corregido}, the
thickness of the structure, the optimal overlap of two consecutive
PBGs and the average reflectance. The first block corresponds to
sub-mirrors with a constant number of periods, while the second block
corresponds to sub-mirrors with a variable number of periods according
to the design wavelength. \notaL{No entiendo nada: qué dejaste 
	fijo y qué permitiste variar para optimizar en cada bloque de la tabla?}
\notaV{En el primer bloque \'{u}nicamente se optimiz\'{o} el traslape de dos PBGs consecutivos. En el segundo bloque, se optimizaron el n\'{u}mero de periodos (de 4 a 10 periodos) de los subespejos sintonizados a $\lambda_{D} \geq 800$ nm y el traslape de dos PBGs consecutivas.} 
\begin{table}[htbp]
  \begin{center}
    \caption{Parameters that maximize $\braket{R}$ for  stacked sub-mirrors.}
    \label{tab:table2}
    \begin{tabular}{|c|c|c|c|c|}
      \hline % <-- Toprule here
      \textbf{$p$}&{\textbf{$N$}} &\textbf{Thickness}&\textbf{Overlap}&$\braket{R}$\\
			&&($\mu$m)& \textbf{PBG $\%$}&$\%$\\
      \hline
      1&98&43.2&95&91.0\\
      3&31&42.5&81&91.8\\
      5&17&41.9&68&92.0\\
      \hline
      4&25&38.7&74&92.3\\\textcolor{red}{6}&\textcolor{red}{18}&\textcolor{red}{41.5} &\textcolor{red}{78} & \textcolor{red}{95.35}\\
      10&13&45.4&56&95.34\\
      \hline
    \end{tabular}
  \end{center}
\end{table}

According to table \ref{tab:table2}, the structure that has the highest
reflectance is in the second block, with an optimal overlap between
consecutive PBGs of $78\%$, a thickness of
41.5 $\mu$m, and  average reflectance $\braket{0.953}$. It is made up
of 18 sub-mirrors tuned to the following wavelengths
400, 460, 510, 570, 640, 720, 810, 910, 1020, 1150, 1290, 1450, 
1630, 1830, 2060, 2320, 2610, and 2860 nm.
We synthesized this structure and designated it {\em sample $S_3$}.
Its calculated and measured
reflectance spectra are shown in Fig. \ref{Fig3}.
\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]
{F3Alternativa.pdf}
\end{center}
\caption{ (a) Calculated reflectance $R(\lambda,\theta)$ for non-polarized light of the optimized structure $S_3$
  as a function of wavelength $\lambda$ and incidence angle
  $\theta$. (b) Measured and calculated reflectance spectra at several
  angles of incidence $\theta=10^\circ$, $20^\circ$,
  $30^\circ$, $40^\circ$, $50^\circ$, $60^\circ$. The gray band indicates
  the region in which the reflectance is greater than $R>0.90$.  Inset shows a
  photograph with a top view of the synthesized structure.}
\label{Fig3}
\end{figure}

Fig. \ref{Fig3}(a) reveals a quasi omnidirectional
mirror in the range from 950 to 2900 nm, with an angular range between $0^\circ$ and
$60^\circ$. It is also observed that at incidence angles $\theta
>70^\circ$ and long
wavelengths the reflectance decreases and has oscillations, which are attributed to the
greater penetration of the electromagnetic field within the structure, as shown by
Puente-D\'{\i}az, et al. \cite{Puente2020}. In Fig. \ref{Fig3}(b) we compare the
calculated and measured reflectance for the structure $S_3$ at several angles of
incidence. Although, the quasi omnidirectional wavelength range of the synthesized
structure is slightly smaller than the calculated one, from 950 to 2750 nm, the measured
PBG is almost twice as wide as a recently reported PS chirped
structure \cite{Chavez2020}. \notaL{Por qué comparamos con ésta? 
	¿Era la mejor que había? Habría que decirlo}
\notaV{S\'{i}, es la estructura, a base de SP, que tiene el mayor ancho OD}

Finally, Table \ref{tab:table3} shows some porous silicon based OD mirrors designed to operate in the NIR
region and the width of the omnidirectional band gaps are compared
with those of the structures
analyzed in the present study. The table reveals that the porous silicon based
structures $S_2$ and $S_3$ have the widest gap widths, 1.36 times greater than the
largest reported work until now in the NIR region \cite{Wu2021}.

>>>>

The function
$f_{3}$ yields after optimization the highest $\braket{R}$ in the
region $\mathcal R_1$ with the thinnest structure (see table
\ref{tab:tableA}). Furthermore, this structure has a calculated OD gap
\notaL{I'm unsure about the nomenclature ``gap''. I guess it is
  theoretical, right?}
 \notaV{Podr\'{i}a utilizar el t\'{e}rmino "OD width" para referirme al ancho omnidireccional del espejo}
of 250 nm centered at 1125 nm with a
reflectance
$R>0.90$, as shown in Fig. \ref{Fig1}(b). We
synthesized a structure  designated {\em sample $S_1$} corresponding
to these results. For the region $\mathcal R_2$ the
resulting structures have similar thicknesses and attain similar reflectance
spectra, though the one with the smallest thickness and the maximum
reflectance is that obtained from the family $f_{1}$. We
also synthesized the corresponding
structure and designated it {\em sample $S_2$}. The
calculated optimized reflectance spectrum is shown in Fig. \ref{Fig1}(d).
This structure has a very wide region where $ R(\lambda, \theta)>
0.90$, which goes from 850 to 3000 nm in an angular range
from $0^\circ$ to $70^\circ$. Thus, it has a
quasi-OD (q-OD) gap of 2150 nm centered at 1925 nm.
The functions $f_i$ optimized for the region $\mathcal R_1$ are shown
in Fig. \ref{Fig1}(a), and those for $\mathcal R_2$
in Fig. \ref{Fig1}(c). The profiles $f_i$ are qualitatively
similar. For example, for $\mathcal R_1$ the optimal photonic
structures have a small number of periods tuned to the wavelengths where
silicon has a large absorption, i.e.,  the first periods of the
structure.
As in $\mathcal R_2$ the absorption of porous silicon is negligible,
the periods are distributed quasi-evenly. \notaL{Sigo sin
  entender. ¿La absorción del silicio poroso depende de la muestra?
  ¿Qué significa quasi-evenly? Quité el 'due', pues era mala redacción}

@@

We measured the reflectance spectra of samples $S_1$ and $S_2$
at various angles of incidence $\theta$. Due to
experimental limitations, we restrict our results to the case of
unpolarized light. In Fig. \ref{Fig2}(a), the calculated and measured
reflectance corresponding to sample $S_1$ are compared from 350 to 1400 nm for different angles of
incidence ($\theta=10^\circ$, $20^\circ$, $30^\circ$, $40^\circ$,
$50^\circ$, and $60^\circ$). The spectra are qualitatively
similar, and for $\lambda>700$ nm and $10^\circ < \theta <
40^\circ$, they agree quantitatively, with a difference smaller
than $5\%$.
The
measured reflectance is lower than the calculated one, more so at
small wavelengths and large angles. This difference
may be partially attributed to the scattering of light due to the
roughness present at the sample
\cite{Theiss1994,Chavez2020,Ortiz2020} that we have not taken into
account in our theory. Due to the limitations of our
spectrophotometer, we couldn't perform measurements for $\theta>60^\circ$ and thus
check the OD gap. Nevertheless, our results allow us to conclude that
the structure has a quasi-omni-directional
bandgap (R$\left(\lambda,\theta \right)>0.90$) between 980 and
1340 nm.
\begin{figure}
	\label{Fig2}
	\begin{center}
		\includegraphics[width=\textwidth]{F2Alternativa.pdf}
	\end{center}
	\caption{Reflectance spectra for non-polarized light calculated and measured at different
	angles of incidence $\theta=10^\circ$, $20^\circ$, $30^\circ$,
        $40^\circ$, $50^\circ$, and $60^\circ$ for structure $S_1$
        (panel a)  and $S_2$ (panel b). The gray band indicates the
        region where the reflectance is greater than  $0.90$,
        corresponding to the quasi OD gap of the
        structure. Inset: photograph of the synthesized structure.}
\end{figure}
In Fig. \ref{Fig2}(b) we compare the
calculated and measured spectra of sample $S_2$ in the range
from 400 to 3000 nm.
Both spectra are very similar, with some differences at long
wavelengths which can be
attributed to an increase of imperfections such as wavy layers and
more roughness for deeper layers, due to a more restricted diffusivity
of the electrolyte as the thickness of the structure is increased
\cite{Negro2003,Vincent1993}. According to our results, this
structure has a wide quasi-omnidirectional gap ($R>0.90$) of 1800 nm
centered at 1880 nm.

@@

Another class of techniques for designing good reflectors across a wide spectral range
is to stack sub-mirrors tuned to different wavelengths chosen with
different criteria.
For example, Agarwal et al. \cite{Agarwal2003} proposed a photonic
structure in which 54 sub-mirrors were stacked as follows:\notaL{I
  changed to passive to avoid the fact that Agarwal did the stacking} the
first sub-mirror consisted of 2.5 periods \notaL{This means 5 layers?} tuned to
$\lambda_{1}=700$ nm; the following sub-mirrors were tuned to
wavelengths $\lambda_{j}$ according to the sequence $\lambda_{j+1}
- \lambda_{j}=2+j$ (with its suitable units)\notaL{This is still
  wrong and/or I don't understand. What are these suitable units? Why
  the mistery? $j$ numbers
  periods or sub-mirrors? Do you mean (2+j) nm, such as the sequence
  700, $\lambda_2=700+2+2=704$, $\lambda_3=704+2+3=709\ldots$
  $\lambda_{54}=700+2*53+54*55/2-1=2290$?} with 4 periods for
each of the following periods.
Furthermore, Estrada-Wiese et al. \cite{DelRio2018}
developed a method that combines three stochastic optimization algorithms together with
a  narrow space search methodology to obtain a customized and optimized
PC configuration.

We recall that for a periodic structure, the propagation of
electromagnetic waves is described by the dispersion relation
\begin{equation}
	 \cos (KD) = \frac{1}{2} \text{Tr} \bm M,   \label{Dispersion}
\end{equation}
where $K$ is Bloch's vector, $\bm M$ the transfer matrix of a single
period of thickness $D$ \cite{Mochan1987, Mochan1988,
  Perez2018}. Thus,
whenever $\left\vert\text {Tr} \left(M \right) \right\vert>2$
electromagnetic energy cannot propagate in the periodic system and we
expect a high reflectance for a finite system made of a finite number
of periods. This suggests the following design. We stack submirrors
each made of a few periods of a periodic system such that its photonic band gap
(PBG) overlaps the PBG of the previous and that of the next
submirror. The number of periods of each sub-mirror is an
important parameter. If it is too small, the sub-mirror would be
partially transparent within the PBG. If it is too large, the
resulting structure would be too thick. This is particularly important
for submirrors tuned to shorter wavelengths, for which there is some
absorption. We followed thus two design
strategies: In the first, we considered sub-mirrors each with the same
number $p$ of periods. In the second, a different number of periods was
assigned to each submirror according to the center of its PBG: we chose
a single period for those submirrors $j$ tuned to
$\lambda_{j}<500$ nm, two periods for $500 <\lambda_ {j} < 650$ nm,
three periods for $650<\lambda_ {j}<800$ nm, and for
$\lambda_{j} \geq 800$ nm the number of periods $p$ was varied between
4 and 10. \notaL{¿Por qué no se optimizó $p$? Se podría optimizar para
  cada subespejo?}
In both designs, the degree of overlap of consecutive PBGs was
taken as the parameter to be optimized in order to maximize
the reflectance $\braket{R}$ averaged within the spectral and
angular range $400\text{nm}\le
\lambda\le 3000\text{nm}$ and for $0^\circ\le\theta\le90^\circ$.

Table \ref{tab:table2} shows the optimized values of the average
reflectance $\braket{R}$ for
different choices of the number of periods $p$ of each sub-mirror, as
discussed above, including the resulting number $N_m$ of stacked sub
mirrors, the thickness $d$ of the structure, and the optimal
overlap of consecutive PBGs. The first and second blocks correspond to
the first and second strategies discussed above.
\begin{table}[htbp]
  \begin{center}
    \caption{Total number $N_m$ of stacked submirrors, thickness $d$,
      overlap between consecutive PBG and average reflectance
      $\braket{R}$ for optimized structures designed with a
      number $p$ of periods per submirror (first block) or a number $p$
      of periods for those submirrors tuned to wavelengths
      $\lambda_j\geq 800$nm (second block, see text), for different
      values of $p$. The parameters corresponding to the best design
      are typeset in bold.}
    \label{tab:table2}
    \begin{tabular}{ccccc}
      $p$&$N_m$&$d (\mu\text{m})$&\% overlap&$\braket{R}$\\
      \hline
      \hline
      1&98&43.2&95&91.0\\
      3&31&42.5&81&91.8\\
      5&17&41.9&68&92.0\\
      \hline
      4&25&38.7&74&92.3\\
      \bf 6&\bf 18&\bf 41.5&\bf 78&\bf 95.4\\
      10&13&45.4&56&95.3\\
      \hline
    \end{tabular}
  \end{center}
\end{table}

According to table \ref{tab:table2}, the structure that has the highest
reflectance is in the second block, with an optimal overlap between
consecutive PBGs of $78\%$, a thickness of
41.5 $\mu$m, and an average reflectance $\braket{0.954}$. It is made up
of 18 sub-mirrors tuned to the wavelengths
400, 460, 510, 570, 640, 720, 810, 910, 1020, 1150, 1290, 1450,
1630, 1830, 2060, 2320, 2610, and 2860 nm.
We synthesized this structure and designated it {\em sample $S_3$}.
Its calculated and measured
reflectance spectra are shown in Fig. \ref{Fig3}.
\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]
{F3Alternativa.pdf}
\end{center}
\caption{ (a) Calculated reflectance $R(\lambda,\theta)$ for non-polarized light of the optimized structure $S_3$
  as a function of wavelength $\lambda$ and incidence angle
  $\theta$. (b) Measured and calculated reflectance spectra at several
  angles of incidence $\theta=10^\circ$, $20^\circ$,
  $30^\circ$, $40^\circ$, $50^\circ$, $60^\circ$. The gray band indicates
  the region in which the reflectance is greater than $R>0.90$.  Inset shows a
  photograph with a top view of the synthesized structure.}
\label{Fig3}
\end{figure}

Fig. \ref{Fig3}(a) reveals a quasi omnidirectional
mirror in the range from 950 to 2900 nm, with an angular range between $0^\circ$ and
$60^\circ$. It is also observed that at incidence angles $\theta
>70^\circ$ and long
wavelengths the reflectance decreases and has oscillations, which are attributed to the
greater penetration of the electromagnetic field within the structure, as shown by
Puente-D\'{\i}az, et al. \cite{Puente2020}. In Fig. \ref{Fig3}(b) we compare the
calculated and measured reflectance for the structure $S_3$ at several angles of
incidence. Although, the quasi omnidirectional wavelength range of
the synthesized structure, from 950 to 2750 nm, is slightly smaller than the calculated
one, the measured PBG is almost twice as wide
as a recently reported PS chirped structure \cite{Chavez2020}, which
has the largest previously reported OD width.

Finally, Table \ref{tab:table3} shows some porous silicon based OD
mirrors designed to operate in the NIRy
region and the width of the omnidirectional band gaps are compared
with those of the structures
analyzed in the present study. The table reveals that the porous silicon based
structures $S_2$ and $S_3$ have the widest gap widths, 1.36 times greater than the
largest reported work until now in the NIR region \cite{Wu2021}.
